---
title: "A/B Testing Analysis Limehomes"
author: "Etoma Egot"
date: "7/30/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Definition

A/B Testing is a general methodology used online when you want to test a new product or feature. The goal is to design an experiment that is robust and gives repeatable results so as to make an informed decision to launch or not.

### Assumptions
I.	Test Version A is the control group which depicts the existing products or features on the website.
II.	Test Version B is the experimental group to experiment the new version of product or feature to see if users like it or if it increases hotel bookings (conversions).
III.	Converted – Based on the given dataset, there are two categories defined by logical values (True or false):
  (a)	Converted = True when customer successfully makes a booking 
  (b) Converted = False when customer visits the sites but does not make a booking

### Out of Scope
I.	A/B Testing procedure/process
II.	Type 1 & Type II Errors 
III.	Given that practical significance level is not known or not provided with this case study, there is no basis for making a recommendation based on that.

### Objective
I.	To lay out the conclusions drawn from the results of sample data provided
II.	To make recommendations on possible paths and provide relevant justification.Pcont_A = PExp_B

### A/B Test Hypothesis
#### Null Hypothesis
Both version A and B have the same probability of driving customer booking or conversion. In other words, there is no effect or no difference between version A and B.

#### Alternative Hypothesis
Both version A and B have a different probability of driving customer booking or conversion. There is a difference between version A and B. Version B is better than A in driving customer bookings. PExp_B != Pcont_A  

### Conclusions Drawn from Data
1.	There are 711 hits and 18 conversions for test version A and 720 hits and 33 conversions for test version B.
2.	Relative uplift of 81.04% based on a Conversion rate for A = 2.53%, Conversion rate for B = 4.58 %. Hence B is better than A by 81.04%.
3.	P-value computed for this analysis was 0.03633269 (p < 0.05 or p lower than 5% significance level). Hence, the tests results show strong statistical significance. You can be 95% confident that this result is a consequence of the changes made and not a result of random chance.
4.	The computed pooled data confidence interval (lower = 0.001305794, upper = 0.03972796) does not include zero. The confidence interval of “B” is further away from zero than “A” which further strengthens the recommendation.


## Analysis

1. *Let's use the following Library:*
```{r loading-libs, message=FALSE}
library(tidyverse)
library(extrafont)
```

2a. *Let's load the data into a dataframe `ABTest` for the analysis:*
```{r}
load("c:/Users/egot_/Projects/ABTest/rda/ABTest.rda")

```


3a. *Let's take a subset of conversions for test_version_A:*
```{r}
conversion_subset_A <- ABTest %>% filter(variant == "A" & converted == "TRUE")
```

3b. *Number of Conversions for test_version_A:*
```{r}
conversions_A <- nrow(conversion_subset_A)
```

3c.*Number of Visitors for test_version_A:*
```{r}
visitors_A <- nrow(ABTest %>% filter(variant == "A"))
```

3d. *Let's compute conversion rate for test_version_A:*
```{r}
conv_rate_A <-  (conversions_A/visitors_A)  
conv_rate_A

```

3e. *Let's take a subset of conversions for test_version_B:*
```{r}
conversion_subset_B <- ABTest %>% filter(variant == "B" & converted == "TRUE")
```

3f. *Number of Conversions for test_version_B:*
```{r}
conversions_B <- nrow(conversion_subset_B)
```

3g.*Number of Visitors for test_version_B:*
```{r}
visitors_B <- nrow(ABTest %>% filter(variant == "B"))
```

3h. *Let's compute conversion rate for test_version_B:*
```{r}
conv_rate_B <-  (conversions_B/visitors_B)  
conv_rate_B

```

**Relative Uplift**

4. *Let's Calculate Relative uplift in Conversion Rate:*

```{r Relative Uplift, message= FALSE}
uplift <- (conv_rate_B - conv_rate_A)/ conv_rate_A * 100
uplift 
```
Deduction: B is better than A by 81%. This is high enough to decide a winner but we need more supporting evidence before we can arrive at a final decision.

**Pooled Probability for Test Versions A & B**

5a. *Let's compute pooled probability:* 
```{r}
p_pool <- (conversions_A + conversions_B)/(visitors_A + visitors_B)
p_pool
```

5b. *Let's compute the standard error (SE_pool) for the pool:*
```{r}
SE_pool<- sqrt(p_pool*(1-p_pool) * ((1/visitors_A) + (1/visitors_B)))
SE_pool
```

5c. *Let's compute the margin of error for the pool:*
```{r}
MOE <- SE_pool * qnorm(0.975)
MOE
```

5d. *Point Estimate or Difference in proportion:*
```{r}
d_hat <- conv_rate_B - conv_rate_A
d_hat
```

5e. *Compute the Z-score so we can determine the p-value:*
```{r}
z_score <- d_hat/SE_pool
z_score 
```

**P-Value for Test Version A & B**

5f. *Let's compute _p_value_ using the z_score value:*
```{r compute-p-value, message= FALSE }
p_value <- pnorm(q = -z_score, mean = 0, sd = 1) * 2
p_value

```

5g. *Let's compute Confidence interval for the pool*
```{r}
ci <- c(d_hat - MOE, d_hat + MOE)
ci
ci_lower <- d_hat - MOE
ci_lower 
ci_upper <- d_hat + MOE
ci_upper 
```

6a. *Let's compute Standard Error and Confidence Intervals for Test version A separately*
```{r}
X_hat_A <- conversions_A/visitors_A
X_hat_A 

se_hat_A <- sqrt(X_hat_A*(1-X_hat_A)/visitors_A) 
print(se_hat_A) 

ci_A <- c(X_hat_A - qnorm(0.975)*se_hat_A, X_hat_A + qnorm(0.975)*se_hat_A) 
ci_A 
```

6b. *Let's compute Standard Error and Confidence Intervals for Test version B separately*
```{r}
X_hat_B <- conversions_B/visitors_B
X_hat_B  

se_hat_B <- sqrt(X_hat_B*(1-X_hat_B)/visitors_B) 
print(se_hat_B)

ci_B <- c(X_hat_B - qnorm(0.975)*se_hat_B, X_hat_B + qnorm(0.975)*se_hat_B) 
ci_B 
```

6c. *Let's extract the lower and upper confidence intervals into `lower` and `upper` respectively
```{r}
ci_lower_A <- X_hat_A - qnorm(0.975)*se_hat_A
ci_lower_A
ci_upper_A <- X_hat_A + qnorm(0.975)*se_hat_A
ci_upper_A

ci_lower_B <- X_hat_B - qnorm(0.975)*se_hat_B
ci_lower_B
```

7a. *Let's create a dataframe of results for the pool*
```{r}
vis_result_pool <- data.frame(
  metric=c(
    'Estimated Difference',
    'Relative Uplift(%)',
    'pooled sample proportion',
    'Standard Error of Difference',
    'z_score',
    'p-value',
    'Margin of Error',
    'CI-lower',
    'CI-upper'),
  value=c(
    conv_rate_B - conv_rate_A,
    uplift,
    p_pool,
    SE_pool,
    z_score,
    p_value,
    MOE,
    ci_lower,
    ci_upper
  ))
vis_result_pool
```

7b. *Let's create a dataframe of results per test version*
```{r}
vis_result <- data.frame(variant = c("A","B"), visitors = c(visitors_A, visitors_B),
                         conversions = c(conversions_A,conversions_B),conversion_rate = round(c(conv_rate_A, conv_rate_B),4),
                         Standard_error = round(c(se_hat_A,se_hat_B),5), Conf_Interval_A = c(ci_A[1],ci_A[2]))
vis_result
```

## Visualize the Results

8a. *Let's create the dataframe*
```{r}
ABTdata = data.frame(
  variant = factor(rep(c("A", "B"), each=200)),
  conf_interval = c(rnorm(200, 0.02773925, 0.005891128), rnorm(200, 0.05068493, 0.007793573))
)
head(ABTdata, 4)
```
8b. *Let's create a sub-dataframe we will call in our plot*
```{r}
pe = data.frame(variant = c("A","B"), conversion_rate = round(c(conv_rate_A, conv_rate_B),4), lower_confidence = round(c(ci_lower_A,ci_upper_A),4))
pe
```

8c. *#Let's plot the distributions*
```{r}
a <- ggplot(ABTdata, aes(x = conf_interval))

a + geom_density(aes(fill = variant), alpha = 0.3) +
  geom_vline(aes(xintercept = lower_confidence[1], color = variant),
             data = pe, linetype = "dashed") +
  geom_vline(aes(xintercept = lower_confidence[2], color = variant),
             data = pe, linetype = "dashed") +
  geom_vline(aes(xintercept = conversion_rate, color = variant),
             data = pe, linetype = "dashed") +
  scale_color_manual(values = c("#b8b7b8", "#b8b7b8"))+
  scale_fill_manual(values = c("#e9e8e9", "#4b779d")) +
  annotate(geom="text", x= 0.0507,  y=29, 
           hjust = 0,     # zero left justifies the text annotation horizontally. 0.5 is center, 1 is right justified.  
           vjust = 0.5,   # > +0.1 range pushes the text annotation down vertically
           #alpha = 0.2,  #alpha reduces the transparency of the text
           label="CR B: 5.06%",
           fontface = "bold",
           colour = "black",
           angle = 90,
           family="Century Gothic",
           size = 4.0) +
  annotate(geom="text", x= 0.0277,  y=35, 
           hjust = 0,     # zero left justifies the text annotation horizontally. 0.5 is center, 1 is right justified.  
           vjust = 0.5,   # > +0.1 range pushes the text annotation down vertically
           #alpha = 0.2,  #alpha reduces the transparency of the text
           label="CR A: 2.77%",
           fontface = "bold",
           angle = 90,
           colour = "black",
           family="Century Gothic",
           size = 4.0)+
  annotate(geom="text", x= 0.0403,  y=24, 
           hjust = 0,     # zero left justifies the text annotation horizontally. 0.5 is center, 1 is right justified.  
           vjust = 0.5,   # > +0.1 range pushes the text annotation down vertically
           #alpha = 0.2,  #alpha reduces the transparency of the text
           label="95%",
           #fontface = "bold",
           angle = 90,
           colour = "black",
           family="Century Gothic",
           size = 4.0)+
  annotate(geom="text", x= 0.0164,  y=24, 
           hjust = 0,     # zero left justifies the text annotation horizontally. 0.5 is center, 1 is right justified.  
           vjust = 0.5,   # > +0.1 range pushes the text annotation down vertically
           #alpha = 0.2,  #alpha reduces the transparency of the text
           label="95%",
           #fontface = "bold",
           angle = 90,
           colour = "black",
           family="Century Gothic",
           size = 4.0)+
  labs(title = "Expected Distributions of Variants A and B",
       subtitle = "Variant B's observed conversion rate (5.07%) was 82.72% higher than Variant B's conversion rate (2.77%).\nYou can be 95% confident that this result is a consequence of the changes made and not a result of random chance.",
       x = "Confidence Interval",
       y = "",
       caption = "Etoma Egot") +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.ticks.y = element_blank(), #remove y axis ticks
        axis.title.y = element_blank()) + #remove y axis title
  theme(plot.title = ggplot2::element_text(family="Century Gothic",
                                           size=20,
                                           #face="bold",
                                           color="#002849")) +
  theme(plot.subtitle = ggplot2::element_text(family="Century Gothic",
                                              size=16,
                                              face="bold",
                                              color = "#4b779d"))+
  theme(panel.grid.major.y = ggplot2::element_line(color="#FAFAFA"))

```


9. *Let' visualize the pool using a normal distribution*

```{r}
ABTdata_pool = data.frame(Conf_interval = rnorm(n = 10000, mean = 0, sd = SE_pool))

#Let's plot the distributions
b <- ggplot(ABTdata_pool, aes(x = Conf_interval))

b + geom_histogram(aes(y = ..density..),
                   colour="black", fill="white", binwidth = 0.00029) +
  geom_density(alpha = 0.2, fill = "#FF6666")+
  theme_classic()
```













































































